Identifying regime transitions for water governance at a basin scale

### 2022-04-28 paper/main/01_introduction.tex
docs(discussion): refactor and grammarly check

Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water %! citation.
For populated large river basins, missing governance means missing sustainability, and a first important step in understanding the transitions with successful water governance is identifying the different regimes.
\cite{undpwatergovernancefacilityWaterGovernanceIssue}.
Regime of water governance maintains by concreted intertwines within human-water systems (such as management, institutions, and exploitations), as a stable state in structures and functions
\cite{carpenterEarlyWarningsRegime2011,rochaCascadingregimeshifts2018, gregrCascadingsocialecologicalcosts2020}.
Therefore, as both signals and consequences of substantive changes in human-water systems, regime shifts sometimes leading to new challenges in water governance.
The lack of a comprehensive but straightforward approach to identifying changes in water governance regimes challenges sustainability, and filling this gap can well align human and water systems (Figure~\ref{fig:framework}).

Governance is essentially about ``who gets what, when and how'', the United Nations Development Programme (UNDP) thus suggested three key dimensions of water use are decided by the water governance directly: ``When and what water to use?'' (stress), ``How water provides different services to well-beings?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
\cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}. %! UNDP year
First, water stress depends not only on climate (with increasing scarcity and uncertainty in many regions) but also on the increasingly insatiable demands from economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
\cite{greveGlobalassessmentwater2018,wadaHumanwaterinterface2017,qinFlexibilityintensityglobal2019}.
Second, the purpose of how water services human well-being is to consider trade-offs between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production)
\cite{liuWaterscarcityassessments2017,florkeWatercompetitioncities2018,kleemannQuantifyinginterregionalflows2020}.
Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by systematically regulating
\cite{roobavannanRoleSectoralTransformation2017,speedBasinwaterallocation2013}.
Despite regime shifts in water governance related to substantive changes in any of the three dimensions, separately considering their intertwines within human-water systems can lead to holistic failure in governing water.

The Yellow River Basin (YRB), fifth-largest river in the world, was most in need of integrated water governance because drastically anthropogenic intervention led to intense governance challenges in sustainability (see \textit{Appendix} Methods S1 and Figure S1 for details).
Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the governance issues troubled for thousands years of high sediment loads
\cite{wangReducedsedimenttransport2016,wuEvolutioneffectssocialecological2020}.
However, decreased streamflows and water over-use then led to depletions of the over-burdened river, creating new challenges and new governance practices, including water use regulation and water transfer across basins
\cite{xiaDevelopmentWaterAllocation2012}.
Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB; -``who gets water, when and how‘’ is always an open question for sustainable development
\cite{wangYellowRiverwater2019,wohlfartSocialecologicalchallengesYellow2016}.
Confronting governance challenges induced by environmental, economic, social, and political factors, numerous governance practices have led the YRB to be among the most drastically-governing large river basins worldwide
Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.

% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
Here, we use the three core dimensions (stress, purpose and allocation) and corresponding indicators of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin-scale (see Figure~\ref{fig:framework} and methods).
% 使用案例研究
Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how to analyze the complicated regimes of water governance and their leading causes in a comprehensive but straightforward way.
% 最后总结出一般性框架
Finally, we propose a general regime transition schema as a practical guideline for a coordinated approach to exploring the challenges faced by big river basin governance.

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=0.9\textwidth]{main/framework.png}
	\caption{
		A framework for identifying the water governance regimes and transitions of a hydrosocial cycle.
		\textbf{A:} water governance has three key dimensions (stress, purpose and allocation), each of which has two potential directions (denoted in red) when changing. (1) ``stress'' of water shifts between scarcity and abundance; (2) weighting ``purpose'' of water between consumptive services or non-consumptive uses; (3) ``allocation'' changes between balanced or lopsided.
		\textbf{B:} along with a transition of hydrosocial water cycle, water governance shifts in line with the three dimensions. Combining corresponding indicators, an abrupt change of the IWGI thus indicates a regime shift in water governance.
		% \cite{steffenTrajectoriesEarthSystem2018,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.
	}
	\label{fig:framework}
\end{figure*}

>>>>

Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water %! citation.
For populated large river basins, missing governance means missing sustainability, and a first important step in understanding the transitions with successful water governance is identifying the different regimes.
\cite{undpwatergovernancefacilityWaterGovernanceIssue}.
Regimes of water governance maintained by concreted intertwine within human-water systems (such as management, institutions, and exploitations), as a stable state in structures and functions
\cite{carpenterEarlyWarningsRegime2011,rochaCascadingregimeshifts2018, gregrCascadingsocialecologicalcosts2020}.
Therefore, regime shifts sometimes lead to new water governance challenges as both signals and consequences of substantive changes in human-water systems.
The lack of a comprehensive but straightforward approach to identifying changes in water governance regimes challenges sustainability, and filling this gap can well align human and water systems (Figure~\ref{fig:framework}).

Governance is essentially about ``who gets what, when and how''. The United Nations Development Programme (UNDP) thus suggested that three key dimensions of water use are decided by the water governance directly: ``When and what water to use?'' (stress), ``How does water provides different services to well-beings?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
\cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}. %! UNDP year
First, water stress depends not only on climate (with increasing scarcity and uncertainty in many regions) but also on the increasingly insatiable demands from economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
\cite{greveGlobalassessmentwater2018,wadaHumanwaterinterface2017,qinFlexibilityintensityglobal2019}.
Second, the purpose of how water services human well-being is to consider trade-offs between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production)
\cite{liuWaterscarcityassessments2017,florkeWatercompetitioncities2018,kleemannQuantifyinginterregionalflows2020}.
Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by systematically regulating
\cite{roobavannanRoleSectoralTransformation2017,speedBasinwaterallocation2013}.
Despite regime shifts in water governance related to substantive changes in any of the three dimensions, separately considering their intertwines within human-water systems can lead to holistic failure in governing water.

The Yellow River Basin (YRB), the fifth-largest river in the world, was most in need of integrated water governance because drastically anthropogenic intervention led to intense governance challenges in sustainability (see \textit{Appendix} Methods S1 and Figure S1 for details).
Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the governance issues troubled by thousands of years of high sediment loads
\cite{wangReducedsedimenttransport2016,wuEvolutioneffectssocialecological2020}.
However, decreased streamflows and water over-use then led to depletions of the over-burdened river, creating new challenges and new governance practices, including water use regulation and water transfer across basins
\cite{xiaDevelopmentWaterAllocation2012}.
Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB; -``who gets water, when and how‘’ is always an open question for sustainable development
\cite{wangYellowRiverwater2019,wohlfartSocialecologicalchallengesYellow2016}.
Confronting governance challenges induced by environmental, economic, social, and political factors, numerous governance practices have led the YRB to be among the most drastically-governing large river basins worldwide
Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.

% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
Here, we use the three core dimensions (stress, purpose and allocation) and corresponding indicators of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin-scale (see Figure~\ref{fig:framework} and methods).
% 使用案例研究
Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how to analyze the complicated water governance regimes in a comprehensive but straightforward way.
Following synthetic analyses of the changes in water demand, supply, economic outcomes, and institutions, we interpret the leading causes of the regime shifts.
% 最后总结出一般性框架
Finally, we propose a general regime transition schema as a practical guideline for a coordinated approach to exploring the challenges faced by big river basin governance.

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=0.9\textwidth]{main/framework.png}
	\caption{
		Identifying the water governance regimes in transitions of a hydrosocial cycle.
		\textbf{A.} Water governance has three key dimensions (stress, purpose and allocation), each of which has two potential directions (denoted in red) when changing. (1) ``stress'' of water shifts between scarcity and abundance; (2) weighting ``purpose'' of water between consumptive services or non-consumptive uses; (3) ``allocation'' changes between balanced or lopsided.
		\textbf{B.} Along with a transition in hydrosocial water cycle, water governance shifts in line with the three dimensions. Combining corresponding indicators, an abrupt change of the IWGI thus indicates a regime shift in water governance.
		% \cite{steffenTrajectoriesEarthSystem2018,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.
	}
	\label{fig:framework}
\end{figure*}

### 2022-04-28 paper/main/03_results.tex
docs(discussion): refactor and grammarly check

% 这一节主要展示IWGI的变化趋势和WUR的划分
Two significant breakpoints divide the changes in the IWGI into three periods, with different contributions from three dimensions (Figure~\ref{fig:IWGI}A).
% 第一阶段
In the first period (P1, 1965-1978), the IWGI decreased rapidly.
While the indicator of purpose and allocation contributed more to the IWGI ($49.45\%$ and $34.95\%$ on average, respectively), the remarkable downward trend correlates significantly ($p<0.01$) to the decreasing allocation and stress indicators (Figure~\ref{fig:IWGI}B).
% 第二阶段
In the second period (P2, 1979-2001), the increasing stress indicator significantly ($p<0.01$) contributed to the upward IWGI, while the allocation and purpose indicators played negative roles in changing the IWGI.
% 第三阶段
During the third period (P3, 1995-2013), while the stress indicator kept its biggest share in contributions ($57.11\%$ on average), the increased allocation indicator and decreased purpose indicator changed the regime of IWGI.
% Overall
Taken together, the overall features of the three dimensions in different periods is relative to a directional change in the combination of three dimensions (Figure~\ref{fig:IWGI}C).
The results suggest three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001), and an adaptation oriented regime (P3: 2002-2013).

@@

% 进一步挖掘IWGI变化的根本原因，
The underlying causes of changes in the IWGI are associated with various factors but are different in the two regime shifts.
% 灌溉区扩张和工业和服务业的经济增长是P1和P2目的变化的关键。
Changing water demands and supply were critical to the shift between P1 and P2.
% P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
As the dominant water demand during the massive supply regime (P1), the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), simultaneously supported by increasing supply through the constructions of reservoirs (\textit{SI Appendix} Fig. S3).
% 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
Entering the transformation governance regime (P2), however, the expansion of irrigated areas slowed down, and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to an $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).

% 水分利用效率由P2变化到P3。
From P2 to P3, the efficiency of water use changed obviously.
Not only irrigated areas keep their slow expansion in the adaptation oriented regime (P3) (Figure\ref{fig:Causes}A), but industry and urban services also assumed a more vital economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Fig. S4), both experienced significant declines in water use for a unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
As a result, the differences between sectors of water use reduced while the total water stress remained stable during P3 (\textit{SI Appendix} Fig. S3).

% 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
Environmental context, social transformation and policies played roles in all three regimes.
We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during the massive supply regime (R/B ratios were significantly higher, see Figure~\ref{fig:Causes}C, $p<0.01$), when natural water resources were also relatively abundant (\textit{SI Appendix} Fig. S5).
Since the transformation governance regime (P2), the number of new reservoirs decreased significantly and significantly increased basinal policies rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{SI Appendix} Fig. S6).
In the adaptation oriented regime, authorities proposed more national-level water governance policies under the guidance of national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
The regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.

>>>>

% 这一节主要展示IWGI的变化趋势和WUR的划分
Two significant breakpoints divide the changes in the IWGI into three periods, with different contributions from three dimensions (Figure~\ref{fig:IWGI}A).
% 第一阶段
In the first period (P1, 1965-1978), the IWGI decreased rapidly.
While the indicator of purpose and allocation contributed more to the IWGI ($49.45\%$ and $34.95\%$ on average, respectively), the remarkable downward trend correlates significantly ($p<0.01$) to the decreasing allocation and stress indicators (Figure~\ref{fig:IWGI}B).
% 第二阶段
In the second period (P2, 1979-2001), the increasing stress indicator significantly ($p<0.01$) contributed to the upward IWGI, while the allocation and purpose indicators played negative roles in changing the IWGI.
% 第三阶段
During the third period (P3, 1995-2013), while the stress indicator kept its most prominent share in contributions ($57.11\%$ on average), the increased allocation indicator and decreased purpose indicator changed the regime of IWGI.
% Overall
Taken together, the overall features of the three dimensions in different periods are relative to a directional change in the combination of three dimensions (Figure~\ref{fig:IWGI}C).
The results suggest three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001), and an adaptation oriented regime (P3: 2002-2013).

@@

% 进一步挖掘IWGI变化的根本原因，
The underlying causes of changes in the IWGI are associated with various factors but are different in the two regime shifts.
% 灌溉区扩张和工业和服务业的经济增长是P1和P2目的变化的关键。
Changing water demands and supply were critical to the shift between P1 and P2.
% P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
As the dominant water demand during the massive supply regime (P1), the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), simultaneously supported by increasing supply through the construction of reservoirs (\textit{SI Appendix} Fig. S3).
% 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
Entering the transformation governance regime (P2), however, the expansion of irrigated areas slowed down, and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to an $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).

% 水分利用效率由P2变化到P3。
From P2 to P3, the efficiency of water use changed obviously.
Not only irrigated areas keep their slow expansion in the adaptation oriented regime (P3) (Figure\ref{fig:Causes}A), but industry and urban services also assumed a more vital economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Fig. S4), both experienced significant declines in water use for a unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
As a result, the differences between sectors of water use reduced while the total water stress remained stable during the adaptation oriented regime (\textit{SI Appendix} Fig. S3).

% 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
Environmental context, social transformation and policies played roles in all three regimes.
We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during the massive supply regime (R/B ratios were significantly higher, see Figure~\ref{fig:Causes}C, $p<0.01$), when natural water resources were also relatively abundant (\textit{SI Appendix} Fig. S5).
Since the transformation governance regime (P2), the number of new reservoirs decreased significantly and significantly increased basinal policies rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{SI Appendix} Fig. S6).
In the adaptation oriented regime, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
The regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.

### 2022-04-28 paper/main/04_discussion.tex
docs(discussion): refactor and grammarly check

% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
Our results show that there have been three distinct but sequential governance regimes within the YRB: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and an adaptation oriented regime (P3: 2002-2013).
Furthermore, shifts between these regimes were caused by different environmental, economic, social or political drivers, deciding who gets water, when and how.
The process echoes how social systems can change water governance regimes by enhancing their adaptive capacity. %! citation
However, the IWGI quantitatively identifies and reveals that abstract pattern, thus characterizing the transition of water governance in detail for the first time.
It is important to note that each indicator or cause changes gradually, but emerging regime shifts move water governance along with the hydrosocial water cycle at a basin scale.
As a result, the water governance challenges were primarily economic and environmental at the beginning of the trajectory and social and policy-related towards the end (Figure~\ref{fig:summary} C and D).

% 在水资源压力较低的大规模供应制度(长江流域1965-1978年)期间，水治理实践倾向于通过建设水库和渠道来增加服务用水(当时主要是供应目的——牲畜和农作物)。
During the massive supply regime with lower water stress (1965-1978 in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
% 然而，正如“人类将征服自然”的流行口号所暗示的那样，水供应的增加很少考虑到人水关系不可逆转的变化，从而也急剧增加了水的需求，很少考虑到流域的保护。
As the popular slogan ``man will conquer nature'' suggested, however, the enhancement of water supply aligned with little consideration of the irreversible changes in the human-water relationship, thus drastically increasing water demand with little consideration in basinal conservation.
\cite{zhouDecelerationChinahuman2020}.
% 在那十年里，灌溉农田和引水设施的迅速扩张，使负担过重的长江水利枢纽接近临界点，在这个临界点上，持续增加供应来满足无限的需求是不现实的
The rapid expansion of irrigated farmland and water diversion facilities in that decade brought the overburdened YRB close to the critical point, where keeping increasing supply to meet the unlimited demand is unpractical
% 结果，自1972年以来，超过80%的地表水使用量导致了河流的频繁枯竭，随之而来的是生态问题，如湿地的萎缩和生物多样性的下降。
As a result, the over 80\% surface water use then led to river depletions frequently since 1972, with ecological issues, such as wetlands shrinkage and declines in biodiversity.
% 此外，由于处于上升阶段的工业经济也受到水资源压力的限制，现有的水治理模式严重导致了巨大的社会-生态危机和对可持续性的重大挑战
In addition, as the water stress also limited the industrial economy in the ascendant, the existing modes of water governance led to a social-ecological crisis and challenged sustainability rigorously
\cite{wohlfartRiverBasinCourse2016}.

@@

Finally, it came into an adaptation-oriented regime (P3: 2002-2013), when drastically shifting in societies occurred with stable water stress.
Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
\cite{dalinBalancingwaterresource2015}.
Reconstruction of resources widespread in different industries and regions was calling for adaptation in water governance, where the urgent requirements of adjusting the rigid quota shares from the previous regime can be an example.
% 类似的，此稳态下国家层面的水治理政策都在进行补充或调整，因为这种制度的缺失和社会的不公平正成为流域新的治理挑战。
Like this, many national-level governing practices were proposed under the regime because the absence of such policies with the social dilemma of high-quality development became new structural challenges for water governance
\cite{konarExpandingScopeFoundation2019}.

% 一般来说，在向水社会循环的转变过程中，三种治理制度之间的转变是依次发生的。
In general, the shift between the governance regimes advances in parallel with the trajectory of the hydrosocial cycle (Figure~\ref{fig:summary}A, B and C).
The transition from biophysical control to social and institutional control of ecosystem dynamics may become increasingly widespread in social-ecological systems as increasing anthropogenic impacts gradually change the world
\cite{bestPaceHumanInducedChange2020,cummingLinkingeconomicgrowth2018,cummingImplicationsagriculturaltransitions2014}.
With intensive anthropogenic intervention, the YRB may be the most prominent example in this general transition of water governance -``improving supply, transforming governance, and enhancing adaptation'' %! Citation.
The transition regimes identified here also echo the two kinds of major water governance challenges globally (resource challenges and structural challenges, Figure~\ref{fig:summary} and \textit{SI Appendix} Fig. S9)
\cite{singhWaterGovernanceChallenges2019,porcherFacingChallengesWater2019}.
Our analysis suggests that the early phase of transition often leads to resource-focused challenges that result from economic and environmental change, while structural challenges dominate the later phases of governance in social and political aspects.
Resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins
\cite{allanNavigatingcomplexitiescoordinated2019,florkeWatercompetitioncities2018,liuWaterSustainabilityChina2012}.
Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and maybe in urgent need of novel flexible, efficient sociopolitical governance structures %! Kitroeff citation wrong
\cite{kitroeffThisWarCrossBorder2020,kitroeffThisWarCrossBorder2020,roobavannanRoleSectoralTransformation2017,unep-dhiTransboundaryRiverBasins2016}.
Typically, resource and structural challenges occur sequentially during the transition of water governance within the YRB.
From the perspective of the core dimensions emphasized by the UNDP for water governance, our proposed schema connects governance challenges and the transformation of large river basins toward a hydrosocial water cycle.

\subsection{Implications, limitations, and future directions}
\label{Outlook}

% Implications
Water governance gradually becomes a national or international concern from a primarily local concern because large river basins are critical sources of ecosystem services, economic development, and human well-being.
As the ubiquitous tele-coupling is rising additional water governance challenges in the tighter connected world, the transition of hydrosocial cycle and regime shifts align with different human-water relationships.
Within the growing hydro-social cycle, the IWGI index depicts the increase of the adaptive capacity and sketches the transitional water governance regimes in a relatively straightforward but comprehensive way.
It is important for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily useful under a different regime
%! \cite{cummingLinkingEconomicGrowth2018, reyersSocialEcologicalSystemsInsights2018}.
In the case of the YRB, an essential institution of water quota in the governance transforming regime became rigid during the enhanced adaptation phase.
On the contrary, additional water from the ambitious cross-basins water diversion project, which originated in the phase of massive supply, can play an even more crucial role in today's enhancing adaptation phase.
Overall, applications of IWGI can induce a straightforward understanding of the water governance in the transition of the hydrosocial cycle, as descriptions from some previous conceptual frameworks suggested for all large-scale basins worldwide.

%! limitations
One of the main limitations of applying IWGI is abundant data availability for a long-term period.
For example, we used the stress-flexibility-variability (SFV index) here, one of the most comprehensive indexes, as an indicator of the water stress dimension.
With other indicators, therefore, we obtained various datasets in the YRB: water use in different regions and sectors, streamflows in different reaches, reservoir capacity and completion time, with furthermore information in social, economic, and institutional for interpretation.
It means still a gap between the comprehensively identifying and widespread application of IWGI.
However, we assumed that all water governance issues are relative to ``who gets water, when and how'', so water stress, purposes of water services, and water allocation patterns matter.
We suggest that choices of the indicators for the dimensions can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in understanding the transition of governance regimes.

% direction
For today's world, water-related challenges remain one of the major gaps in our progress towards sustainability, while development-first strategies are still a dominant guideline in many places and maybe in opposition to improving governance
\cite{xuAssessingprogresssustainable2020,liuAerosolweakenedsummermonsoons2017,greveGlobalassessmentwater2018}.
% 虽然大多数大型河流流域随着发展而在水管理技术和水利用效率方面有所改善，但淡水利用仍被认为正在接近人类-水系统可能崩溃的行星边界
Although most large river basins have shown improvements in water management technologies and water use efficiency along with development, freshwater use is still approaching planetary boundaries where human-water systems may collapse
\cite{anExploringeffectsGrain2017,degraafEnvironmentalflowlimits2019,hugginssocialecologicaldimensionschanging2020}.
% 我们的分析展示了这种路径的前方很可能是严峻的水治理挑战。
% 总的来说，这种明显的治理失败可能有两个主要原因。
% Overall, there are probably two main reasons for this apparent failure of governance.
% 首先，农业灌溉效率的显著提高通常伴随着灌溉面积的重新扩大，导致水资源压力的趋势不减(效率悖论)
% First, significant improvement in agricultural irrigation efficiency is usually accompanied by a re-expansion of irrigated area, resulting in an unabated trend of water resources stress (the paradox of efficiency)
\cite{graftonparadoxirrigationefficiency2018}.
% 其次，如果没有成功的治理，以水循环为主导的复杂治理结构可能会导致流域尺度上水资源使用的灵活性降低，破坏社会-生态系统的恢复力
In the future, without successful governance, complicated governance structures dominated by hydrosocial water cycles may result in less flexible water use and undermine the resilience of social-ecological systems at a basin-scale
\cite{qinFlexibilityintensityglobal2019,leviaHomogenizationterrestrialwater2020,grillMappingworldfreeflowing2019}.
% 从这些角度来看，我们需要更好、更全面的策略来应对治理挑战，因为核心问题是复杂而难以管理的
From these perspectives, we need more flexible and comprehensive strategies to address governance challenges because the core problems are dynamic and complex
\cite{steffenemergenceevolutionEarth2020,muneepeerakulemergenceresilienceselforganized2020,bodinCollaborativeenvironmentalgovernance2017,biermannNavigatingAnthropoceneImproving2012}.
% 更深入地了解包含非线性变化、制度和过渡思想的治理，应该有助于将治理的重点转移到维持流域社会-生态系统的恢复力和提高其可持续性。
A deeper understanding of governance that incorporates ideas of non-linear change, regimes, and transitions should help to shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability.

>>>>

% Implications
Water governance gradually becomes a national or international concern from a primarily local concern because large river basins are critical sources of ecosystem services, economic development, and human well-being.
As the ubiquitous tele-coupling is rising additional water governance challenges in the tighter connected world, the transition of hydrosocial cycle and regime shifts align with different human-water relationships.
The process echoes how societies can change governance practices by enhancing their adaptive capacity in the hydrosocial cycle, and the IWGI quantitatively identifies this transition.
It is important for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily useful under a different regime
%* \cite{cummingLinkingEconomicGrowth2018, reyersSocialEcologicalSystemsInsights2018}.

% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
In the case of the YRB, our results show that there have been three distinct but sequential governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and an adaptation oriented regime (P3: 2002-2013).
During the massive supply regime with lower water stress (1965-1978 in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
As the popular slogan ``man will conquer nature'' suggested, however, the enhancement of water supply aligned with little consideration of the irreversible changes in the human-water relationship, thus drastically increasing water demand with little consideration in basinal conservation
\cite{zhouDecelerationChinahuman2020}.
The rapid expansion of irrigated farmland and water diversion facilities in that decade brought the overburdened YRB close to the critical point, where keeping increasing supply to meet the unlimited demand is unpractical
As a result, the over 80\% surface water use then led to river depletions frequently since 1972, with ecological issues, such as wetlands shrinkage and declines in biodiversity.
In addition, as the water stress also limited the industrial economy in the ascendant, the existing modes of water governance led to a social-ecological crisis and challenged sustainability rigorously
\cite{wohlfartRiverBasinCourse2016}.

@@

When it came to an adaptation-oriented regime (P3: 2002-2013), drastically shifting in societies adapted to the stable high water stress.
Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
\cite{dalinBalancingwaterresource2015}.
Reconstruction of resources widespread in different industries and regions was calling for adaptation in water governance, where the urgent requirements of adjusting the rigid quota shares from the previous regime can be an example.
Like this, many national-level governing practices were proposed under the regime because the absence of such policies with the social dilemma of high-quality development became new structural challenges for water governance
\cite{konarExpandingScopeFoundation2019}.

% 总体而言，长江流域的水治理是“改善供给、转变治理、增强适应”的水社会循环总体转型中最突出的例子之一。
In general, water governance of the YRB is among the most prominent example in the general transition of hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
With each dimension changing gradually, the emergence of regime shifts drives the water governance challenges at a basin-scale: primarily economic and environmental before the transformation but social and policy-related towards the end (Figure~\ref{fig:summary}) \cite{singhWaterGovernanceChallenges2019,porcherFacingChallengesWater2019}.
In the analogy at a global scale, the resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins
\cite{allanNavigatingcomplexitiescoordinated2019,florkeWatercompetitioncities2018,liuWaterSustainabilityChina2012}.
Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures %* Kitroeff citation wrong
\cite{kitroeffThisWarCrossBorder2020,kitroeffThisWarCrossBorder2020,roobavannanRoleSectoralTransformation2017,unep-dhiTransboundaryRiverBasins2016}.
Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.

%* limitations & direction
One of the main limitations in the approach is the few data worldwide with a long-term period, which means still a gap between the comprehensively identifying and widespread application of IWGI.
However, we assumed that all water governance issues are relative to ``who gets water, when and how'', so water stress, purposes of water services, and water allocation patterns matter.
We suggest that choices of the indicators for the dimensions, therefore, can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in understanding the transition of governance regimes holistically
\cite{steffenemergenceevolutionEarth2020,muneepeerakulemergenceresilienceselforganized2020,bodinCollaborativeenvironmentalgovernance2017,biermannNavigatingAnthropoceneImproving2012}.
In today's world, the regime shifts from biophysical to hydrosocial control of dynamics may become increasingly widespread, so the comprehensive strategies to address governance challenges have become the core of complex human-water systems
\cite{bestPaceHumanInducedChange2020,cummingLinkingeconomicgrowth2018,cummingImplicationsagriculturaltransitions2014}.
Although river basins have shown improvements in water management technologies and water use efficiency, many of them are still approaching planetary boundaries where human-water systems may collapse
\cite{anExploringeffectsGrain2017,degraafEnvironmentalflowlimits2019,hugginssocialecologicaldimensionschanging2020}.
A deeper understanding of governance that incorporates ideas of non-linear regime shifts and transformations should help to shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability.
